---
title: "p8105_hw6_yl4924"
author: "Yongzheng Li"
date: "2022-12-3"
output: github_document
---

# Apply package and inital setup
```{r}
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


# Problem 2

### Import and Clean the homicide dataset
```{r}
url <- "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data <- read_csv(url) %>% 
  janitor::clean_names() %>%
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) %>% 
  unite("city_state", c(city, state), sep = ", ", remove = FALSE) %>% 
  filter(!(victim_race == "Unknown" | city_state == "Tulsa, AL")) %>% 
  filter(victim_race %in% c("White", "Black"))
```

After convert variable victim_age into numerical variable, it is worth to note that there is `r sum(is.na(homicide_data$victim_age))` number of missing value of victim age.

### GLM for city of Baltimore, MD
```{r}
baltimore_logistic <- 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_race + victim_age + victim_sex, data = ., family = binomial())


baltimore_logistic %>% 
  broom::tidy(conf.int = TRUE) %>% 
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>%
  select(term, log_OR = estimate, OR, contains("conf")) %>% 
  filter(term == "victim_sexMale")
  
```

### GLM for all cities in homicide dataset
```{r}
nest_logistic_res =
  homicide_data %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = purrr::map(data, ~glm(resolved ~ victim_race + victim_age + victim_sex, data = .x, family = binomial())),
    result = map(models, ~broom::tidy(.x, conf.int = TRUE))) %>% 
  unnest(result) %>% 
  mutate(
   OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  select(city_state, term, OR, contains("conf")) %>% 
  filter(term == "victim_sexMale") 
```


### plot
```{r}
nest_logistic_res %>% 
  mutate(
    city_state = forcats::fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(title = "Estimated ORs & CIs for Solving Homicides Comparing Male Victims to Female Victims",
       y = "Estimated ORs")

```

From the plot, New York, NY has the lowest estimated OR for solving homicides comparing male victims to female victims(around 0.25). City Albuquerque, NM has the highest OR for solving homicides comparing male victims to female victims(around 1.75). No city solving homicides for males victims is significantly higher than solving homicides for female victims. In contrast, there is `r sum(nest_logistic_res$conf.high <1)` number of cities solving homicides for males victims is significantly lower than solving homicides for female victims.


# Problem 3

### import and clean dataset
```{r}
birthweight <- 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    malform = factor(malform, labels = c("absent", "present")),
    mrace = factor(mrace, labels = c("White", "Black", "Asian", "Puerto Rican")),
    frace = factor(frace, labels = c("White", "Black", "Asian", "Puerto Rican", "Other")),
    babysex = factor(babysex, label = c("male", "female"))) %>%
  drop_na()
```

variable malform, mrace, frace, babysex is category variable, I convert them from numercial to factor variable. 

### Regression model for birthweight

```{r}
model_1 <- lm(bwt ~ blength + gaweeks + smoken + momage + ppbmi, data = birthweight)
birthweight %>% 
  add_predictions(model_1) %>% 
  add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

This model is based on hypothesized structure for the factors that underly birthweight, the main effect include variables: baby length and gestational age controlling for variables: number of  cigarettes smoked per day during pregnance, mother's age at deliver, and mother’s pre-pregnancy BMI. From resdiual vs fited value plot, most data are centered around residual = 0. There are few data points has residual > 1000. These data points need more investigation.

### Compare models
```{r}
cv_df <- 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df <-
  cv_df %>% 
  mutate(
    main_model = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    my_model = map(train, ~lm(bwt ~ blength + gaweeks + smoken + momage + ppbmi, data = .x)),
    interaction_model = map(train, ~lm(bwt ~ blength * bhead * babysex , data = .x))) %>% 
  mutate(
    rmse_main = map2_dbl(main_model, test, ~rmse(model = .x, data = .y)),
    rmse_my = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(interaction_model, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

From the violin plot, the model that include all interactions clearly has higher predictive accuracy gaining by model is more complex compare to other 2 models. 


